Numerical analysis of the influence of magnetic field waveforms on the performance of active magnetic regenerators \thanks{ An abridged version of this manuscript was presented at the ABCM International Congress of Mechanical Engineering (COBEM \colorbox{yellow}{Completar... cidade etc}). }

### 2019-11-03 PaperMagneticProfiles_JBSMSE.tex
Confirm JRB explanation on the multilayer materials.

The casing heat transfer term $\rate{q}\ped{csg}$ in \autoref{eq:78} is calculated solving the heat conduction equation in the regenerator casing \cite{bib:trevizoli16_perfor_model}. It can be neglected in some circumstances if an insulating casing material is assumed, which greatly simplifies the analysis. %More details are provided in \autoref{sec:results-discussions}.

@@

\noindent where \(g(t)\) is a dimensionless function that expresses the mathematical waveform of the pressure gradient, and  \(A\ped{t}\) is its amplitude,  adjusted in a convergence loop. In this loop, the mass flow rate calculated in term of the Darcy velocity from \autoref{eq:75} is compared with the input   mass flow rate until convergence is obtained. %The waveform $g(t)$ represents the fluid flow profile used.

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=8cm]{mprofile}
  \caption{Instantaneous fluid flow profile}
  \label{fig:mprofile}
\end{figure}

@@

For the multilayer simulations, alloys of gadolinium and yttrium are used in the form \ce{Gd_{1-x}Y_x}, where $x$ is the yttrium fraction.  This fraction reduces the Curie temperature of the alloy relative to that of pure gadolinium. Due to the lack of experimental  data on the magnetocaloric properties of \ce{Gd_{1-x}Y_x} alloys at the time this analysis was made, a simpler approach was used in which the \textcolor{blue}{dependence of magnetization, specific heat capacity and entropy with respect to the magnetic field for} alloys with a low yttrium fraction are identical to those of pure gadolinium, \textcolor{blue}{but are shifted to a lower} Curie temperature (corresponding to the yttrium fraction).

\colorbox{yellow}{Fabio, veja se o texto acima estah ok...}

>>>>

The casing heat transfer term $\rate{q}\ped{csg}$ in \autoref{eq:78} is calculated solving the heat conduction equation in the regenerator casing \cite{bib:trevizoli16_perfor_model}. It can be neglected in some circumstances if an insulating casing material is assumed, which greatly simplifies the analysis.

@@

\noindent where \(g(t)\) is a dimensionless function that expresses the mathematical waveform of the pressure gradient, and  \(A\ped{t}\) is its amplitude,  adjusted in a convergence loop. In this loop, the mass flow rate calculated in term of the Darcy velocity from \autoref{eq:75} is compared with the input   mass flow rate until convergence is obtained.

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=8cm]{mprofile}
  \caption{Instantaneous fluid flow profile. Adapated from \cite{bib:fortkamp20-desig}.}
  \label{fig:mprofile}
\end{figure}

@@

For the multilayer simulations, alloys of gadolinium and yttrium are used in the form \ce{Gd_{1-x}Y_x}, where $x$ is the yttrium fraction.  This fraction reduces the Curie temperature of the alloy relative to that of pure gadolinium. Due to the lack of experimental  data on the magnetocaloric properties of \ce{Gd_{1-x}Y_x} alloys at the time this analysis was made, a simpler approach was used in which the dependence of magnetization, specific heat capacity and entropy with respect to the magnetic field for alloys with a low yttrium fraction are identical to those of pure gadolinium, but are shifted to a lower Curie temperature (corresponding to the yttrium fraction).

\nomenclature[ix]{$x$}{yttrium fraction}
